---
title: "Documentation"
editor: source
execute:
  echo: false
  warning: false
format: 
  html
---

```{r table}
library(tidyverse)
all_data <- targets::tar_read(owe_data)

study_count <- nrow(all_data)

published_study_count <- nrow(filter(all_data, published == 1))

country_count <- all_data %>% 
  count(country) %>% 
  nrow()

data_version <- all_data %>% 
  filter(row_number() == 1) %>% 
  pull(data_version)
```

The own-wage elasticity (OWE) of employment measures the proportional change in a group's employment caused by a minimum wage increase, divided by the proportional change in that group’s average wage.

The **Minimum Wage Own-Wage Elasticity Repository** contains a representative 
estimate of the OWE of employment from every minimum wage study published 
since 1992, with the following restrictions:

1. the study must evaluate the employment effects of changes in the statutory
minimum wage

1. the study must estimate a statistically significant, positive wage effect of the
minimum wage, in addition to estimating the employment effect, for the same group of workers using a similar research design

1. the study must be published after 1992 and include "quasi-experimental" 
or "experimental" variations

1. studies older than 10 years must have been published in an academic journal

1. the study must focus on the United States, United Kingdom, countries in the
European Union, or Canada (we will eventually relax this restriction)

The current version of the repository,  Version `r data_version`, contains 
`r study_count` studies, `r published_study_count` of which are published 
in peer-reviewed journals. A description of Version 1.0 of the repository 
is in the paper

::: {.callout-note}
## Paper
Arindrajit Dube and Ben Zipperer. 2024. 
"Own-Wage Elasticity: Quantifying the Impact of Minimum Wages on Employment".
Working Paper. [NBER Working Paper 32925](http://www.nber.org/papers/w32925>).
:::

For more information, explore a [table](table.html) of all the studies or 
download the underlying [data](download.html). Please don't hesitate to 
[submit](submit.html) any corrections or studies we have accidentally omitted.

If you use the data or this site in your own work, please reference or cite it:

::: {.callout-note}
## Repository source
```{r}
#| output: asis
cat(targets::tar_read(citation_full_md))
```
:::