---
title: "Documentation"
editor: source
execute:
  echo: false
  warning: false
format: 
  html
---

```{r table}
library(tidyverse)
all_data <- targets::tar_read(owe_data)

study_count <- nrow(all_data)

published_study_count <- nrow(filter(all_data, published == 1))

country_count <- all_data %>% 
  count(country) %>% 
  nrow()

data_version <- all_data %>% 
  filter(row_number() == 1) %>% 
  pull(data_version)
```

The own-wage elasticity (OWE) of employment is an estimate of the employment 
change for a given wage change experienced by a group of workers, where in this
case the changes in wages and employment are due to minimum wage increases.

The **Minimum Wage Own-Wage Elasticity Database**, contains a representative 
estimate of the OWE of employment from every minimum wage study published 
since 1992, with the following restrictions:

1. the study must estimate a statistically significant wage effect of the 
policy, in addition to estimating an employment effect

1. studies not published in a peer-reviewed journal or equivalent are omitted
if they are more than 10 years old

1. the study must focus on the US, UK, Germany, or Canada 
(we will eventually relax this constraint!)


The current version of the database,  Version `r data_version`, contains 
`r study_count` studies, `r published_study_count` of which are published 
in peer-reviewed journals. Version 1.0 of the database is described in 
IMAGE AND LINK TO WORKING PAPER.



For more information, explore a [table](table.html) of all the studies or 
download the underlying [data](download.html). Please don't hesitate to 
[submit](submit.html) any corrections or studies we have accidentally omitted.

If you use the data or this site in your own work, please reference or cite it:

::: {.callout-note}
## Source
```{r}
#| output: asis
cat(targets::tar_read(citation_full_md))
```
:::