---
title: "Download the latest data"
editor: source
execute:
  echo: false
---

```{r}
make_md_link <- function(name, url) {
  paste0("[", name, "](", url, ")")  
}

```

`r make_md_link(targets::tar_read(owe_csv_file), targets::tar_read(owe_csv_file))`

## Table of elasticities
[mw_owe_database.csv](mw_owe_database.csv)

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(reactable)

targets::tar_read(owe_data) %>% 
  filter(row_number() == 1) %>% 
  transmute(
    study = "Study name, abbreviated as author-year",
    journal = "Journal",
    owe_b = "Effect size",
    owe_se = "Standard error",
    owe_lb = "Lower bound of 95% confidence interval",
    owe_ub = "Upper bound of 95% confidence interval",
    group = "Group of workers",
    overall = "Covers a very broad group of low-wage workers",
    country = "Country",
    published = "Published in a peer-review journal or equivalent",
    authors = "Full names of authors",
    title = "Title of study",
    url = "URL of study",
    source = "Description of how the OWE was calculated",
    data_version = "Minimum wage OWE database version"
  ) %>% 
  pivot_longer(everything(), names_to = "Column name", values_to = "Column description") %>% 
  reactable(pagination = FALSE)
```
<br/>
See the [documentation](documentation.html) for additional details.

## References
A complete list of the studies in a format convenient for bibliographies: [bibtex](mw_owe_studies.bib) [csv](mw_owe_studies.csv) 

## Citation and use of the data
If you use the data or this site in your own work, please reference or cite it:

::: {.callout-note}
## Source
```{r}
#| output: asis
cat(targets::tar_read(citation_full_md))
```
:::
